A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-01-21 src/tex/ms.tex
Updates from Overleaf

The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain. This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. We adopt the yields of \citet{weinberg_scale_2023}, who use a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau to infer population-averaged yields. The only difference here is that we assume that $20\%$ of Si in the Sun is produced by SNe Ia, which reduces the Si plateau to [Si/Fe]$_{\rm cc}=0.35$ and results in a non-zero value for $y_{\rm SI}^{\rm cc}$, unlike in \citet{weinberg_scale_2023}. Our yields are presented in Table \ref{tab:yields}.

\begin{table}
    \centering
    \caption{Nucleosynthetic yields.}
    \label{tab:yields}
    \include{output/yields.tex}
\end{table}

>>>>

The population-averaged nucleosynthetic yields of CCSNe are still fairly uncertain. 
% This problem is exacerbated by the complexity of the CCSN explosion landscape \citep{sukhbold_core-collapse_2016}. We adopt the yields of \citet{weinberg_scale_2023}, who use a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the observed \aFe plateau to infer population-averaged yields. The only difference here is that we assume that $20\%$ of Si in the Sun is produced by SNe Ia, which reduces the Si plateau to [Si/Fe]$_{\rm cc}=0.35$ and results in a non-zero value for $y_{\rm SI}^{\rm cc}$, unlike in \citet{weinberg_scale_2023}. Our yields are presented in Table \ref{tab:yields}.

\begin{table}
    \centering
    \caption{Nucleosynthetic yield sets.}
    \label{tab:yields}
    \include{output/yields.tex}
\end{table}

Adopting a mean Fe yield per SN Ia of $m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$, the yield set $y/Z_\odot=1$ corresponds to an integrated SN Ia rate of $N_{\rm Ia}/M_\star=\num{1.37e-3}$ M$_\odot^{-1}$, and the higher set $y/Z_\odot=3$ corresponds to $N_{\rm Ia}/M_\star=\num{5.36e-3}$ M$_\odot^{-1}$
